Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-16 write_up/mixfishsim_ecolmod.tex
JJP comments

There is increasing interest in technical solutions such as gear and spatial
closures as measures to reduce unwanted catch \citep{Kennelly2002,
	Catchpole2008, Bellido2011, Cosgrove2019} and adaptive spatial
management strategies have been proposed as a way of reducing over-quota
discards \citep{Holmes2011, Little2014, Dunn2014a}. However, if fisheries are
to reduce unwanted catch through spatial avoidance, an in-depth understanding
of spatiotemporal fishery dynamics is required. Implementation of spatial
measures is hampered by a lack of knowledge of fish and fishery spatiotemporal
dynamics and understanding of the scale at which processes become important for
management. \\

Understanding the correct scale for spatial measures is also crucial as it
enables implementation of effective solutions which minimise economic impact
\citep{Dunn2016}. For example, the problem can be to identify a scale that
promotes species avoidance for vulnerable or low quota species while allowing
continuance of sustainable fisheries for available quota species. Identifying
the correct spatial scale remains a challenge because data on fish location at
high temporal and spatial resolutions is expensive and difficult to collect and
proxies are usually inferred from scientific surveys or commercial catches with
limited spatial and temporal resolution. \\

Identifying appropriate spatial scales for fisheries closures has been a
highlighted as crucial to their success \citep{Costello2010, Dunn2016}.
Inference is hampered where spatial information is coarse due to low resolution
reporting of fisheries catch which is aggregated across larger gridded areas
\citep{Branch2005}. Further, if data does not allow identification of spatial
features it may lead to poorly sited closures which are ineffectual or have
unintended consequences. For example, increased benthic impact on previously
unexploited areas from the cod closure in the North Sea were observed without
the intended effect of reducing cod exploitation
\citep{Rijnsdorp2001,Dinmore2003}).\\

More refined spatiotemporal information has since become available through the
combination of logbook and Vessel Monitoring System (VMS) data \citep{Lee2010,
	Bastardie2010, Gerritsen2012, Mateo2016} and more real-time spatial
management has been possible \citep[e.g.][]{Holmes2011}.  However, fishers
establish favoured fishing grounds through an explore-exploit strategy
\citep{Bailey2018} where they search for areas with high catches and then use
experience to return to areas where they've experienced high catch in the past.
This leads to an inherently biased sampling where target species are
over-represented in the catch as fishers exploit areas of high abundance. \\

To understand the effect of spatiotemporal aggregation of data and fishery
targeting we ask two fundamental questions regarding inference derived from
observational data:

\begin{enumerate}
	\item How does sampling-derived fisheries data reflects the underlying
		community structure? 	
	\item How does data aggregation and source impact on spatial fisheries
	management measures?
\end{enumerate}

To answer these questions we i) develop a simulation model where population
dynamics are highly-resolved in space and time by use of a Gaussian spatial
process to define suitable habitat for different populations.  Precise
locations of the fish being known directly rather than inferred from sampling
or commercial catch, we can use the population model to validate how inference
from fisheries-dependent and fisheries independent sampling relates to the real
community structure in a way we could not with real data. We ii) compare, at
different spatial and temporal aggregations, the real (simulated) population
distributions to samples from fisheries-dependent and fisheries independent
catches to test if these are a true reflection of the relative density of the
populations. We then iii) simulate a fishery closure to protect a species based
on different spatial and temporal data aggregations. \\

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

@@

Recruitment is modelled through a function relating to adult biomass. In
\textit{MixFishSim}, it can be either as a stochastic Beverton-Holt stock-recruit
form \citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, or a stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases.

@@

Population movement is a combination of random (diffusive) movement, governed
by a stochastic process where movement between adjacent cells is described by a
set of probabilities, and directed (advective) movement where at certain times
of year the population moves towards spawning grounds by increasing the
probabilities of moving into the spawning grounds from adjacent cells. We
characterise a set of different fishing fleet dynamics exploiting four fish
populations with different spatial and population demographics. \\

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
\textit{Matérn} covariance structure, where the correlation strength weakens
with distance. This enables us to model the spatial autocorrelation observed in
animal populations where density is more similar in nearby locations
\citep{Tobler1970, F.Dormann2007} and we change the parameters to implement
different spatial structures for the different populations using the
\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
habitat field and combine with a temporally dynamic thermal tolerance field to
imitate two key drivers of population dynamics. Each population was initialised
at a single location, and subsequently moved according to a probabilistic
distribution based on habitat suitability (represented by the normalised values
from the GRFs), temperature and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda * d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
below). \\

During pre-defined weeks of the year the habitat suitability is modified with
user-defined spawning habitat locations, resulting in each population having
concentrated areas where spawning takes place. In the simulations the
populations move towards these cells in the weeks prior to spawning, resulting
in directional movement towards the spawning grounds. \\

An advection-diffusion process controls population movement, with a
time-varying temperature covariate used to change the interaction between time
and suitable habitat on a weekly time-step. Each population $p$ was assigned a
thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$ so that
each cell and population temperature suitability is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma^2_{p}$ the mean and standard deviation of the population
temperature tolerance. \\

@@

Fleet dynamics can be broadly categorised into three components: fleet
targeting - that determined the fleet catch efficiency and preference towards a
particular species; trip-level decisions, that determines the initial location
to be fished at the beginning of a trip; and within-trip decisions, that
determines movement from one fishing spot to another within a trip. Together,
these elements implement an explore-exploit type strategy for individual
vessels to maximise their catch from an unknown resource distribution
\citep{Bailey2018}. The decision to use an individual based model for fishing
vessels was taken because fishers are heterogeneous in their location choice
behaviour due to different objectives, risk preference and targeting preference
\citep{VanPutten2012a}. Therefore in the simulations fleet dynamics reflect
individual experiences rather than pre-defined group dynamics.

@@

Each fleet of \textit{n} vessels was characterised by both a general
efficiency, $Q_{fl}$, and a population specific efficiency, ${Q_{fl, p}}$.
Thus, the product of these parameters [$Q_{fl} \cdot Q_{fl, p}$] affects the
overall catch rates for the fleet and the preferential targeting of one
population over another. This, in combination with the parameter choice for the
step-function defined below (as well as some randomness from the exploratory
fishing process) determined the preference of fishing locations for the fleet.

\subsubsection{Trip-level decisions}

Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
confirmed past activity and past catch rates are strong predictors of fishing
location choice. For this reason, the fleet dynamics sub-model included a
learning component, where a vessel's initial fishing location in a trip was
based on selecting from previously successful fishing locations. This was
achieved by calculating an expected revenue based on the catches from locations
fished in the preceding trip as well as the same month periods in previous
years and the travel costs from the port to the fishing grounds, and choosing
randomly from the top 75 \% of fishing events as defined by the expected
profit, that has a seasonal component.

\subsubsection{Within-trip decisions}

@@

With increasing probability throughout the simulation, fishing locations were
chosen based on experience of profitable catches built up in the same month
from previous years and from the previous trip. 'Profitable' in this context
was defined as the locations where the top 70 \% of expected profit would be
found given revenue from previous trips and cost of movement to the new fishing
location. This probability was based on a logistic sigmoid function with a
lower asymptote of 0 and upper asymptote of 0.95, and a growth rate that
ensures the upper asymptote (where decisions are mainly based on past
knowledge) is reached approximately halfway through the simulation.  \\

@@

Individual habitat preferences and thermal tolerances result in different
spatial habitat use for each population (Figure \ref{fig:9}) and consequently
different seasonal exploitation patterns (Fishing mortality in Figure
\ref{fig:10}).

@@

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
that may differ from the underlying populations. As such, we favoured a minimum
realistic model of the fish populations \citep{Plaganyi2014} taking account of
environmental but not demographic stochasticity, while incorporating detailed
fishing dynamics that take account of different drivers in a mechanistic way.
\\

>>>>

There is increasing interest in technical solutions such as gear and spatial
closures as measures to reduce unwanted catch \citep{Kennelly2002,
	Catchpole2008, Bellido2011, Cosgrove2019} and adaptive spatial
management strategies have been proposed as a way of reducing over-quota
discards \citep{Holmes2011, Little2014, Dunn2014a}. However, if fisheries are
to reduce unwanted catch through spatial avoidance, an in-depth understanding
of spatiotemporal fishery dynamics is required. Implementation of spatial
measures is hampered by a lack of knowledge of fish and fishery spatiotemporal
dynamics and understanding of the scale at which these processes become
important for management. \\

Understanding the correct scale for spatial management measures to be effective
is also crucial as it enables implementation of effective solutions which
minimise economic impact \citep{Dunn2016}. For example, the problem can be to
identify a scale that promotes species avoidance for vulnerable or low quota
species while allowing continuance of sustainable fisheries for available quota
species. Identifying the correct spatial scale remains a challenge because data
on fish location at high temporal and spatial resolutions is expensive and
difficult to collect and proxies are usually inferred from scientific surveys
or commercial catches with limited spatial and temporal resolution. \\

Identifying appropriate spatial scales for fisheries closures has been a
highlighted as crucial to their success \citep{Costello2010, Dunn2016}.
Inference on fisheries spatial dynamics is hampered where spatial information
is coarse due to low resolution reporting of fisheries catch which is
aggregated across larger gridded areas \citep{Branch2005}. Further, if data
does not allow identification of spatial features it may lead to poorly sited
closures which are ineffectual or have unintended consequences. For example,
increased benthic impact on previously unexploited areas from the cod closure
in the North Sea were observed without the intended effect of reducing cod
exploitation \citep{Rijnsdorp2001,Dinmore2003}).\\

More refined spatiotemporal information has since become available through the
combination of logbook and Vessel Monitoring System (VMS) data \citep{Lee2010,
	Bastardie2010, Gerritsen2012, Mateo2016} and more real-time spatial
management has been possible \citep[e.g.][]{Holmes2011}.  However, fishers
establish favoured fishing grounds through an explore-exploit strategy
\citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
and then use experience to return to areas where they've experienced high catch
in the past.  This leads to an inherently biased sampling where target species
are over-represented in the catch as fishers exploit areas of high abundance.
\\

To understand the effect of spatiotemporal aggregation of data and fishery
targeting on our understanding of fish communities we ask two fundamental
questions regarding inference derived from observational data:

\begin{enumerate}
	\item Do different source of sampling-derived fisheries data
		reflects the underlying community structure or represent a
		biased picture? 	
	\item How does data aggregation and data source impact on the success
		of spatial fisheries management measures?
\end{enumerate}

To answer these questions we i) develop a simulation model where population
dynamics are highly-resolved in space and time, using a Gaussian spatial
process to define suitable habitat for different populations. As the precise
locations of the fish are known directly rather than inferred from sampling
or commercial catch, we can use the population model to validate how inference
from fisheries-dependent and fisheries independent sampling relates to the real
community structure in a way we could not with real data. We ii) compare, at
different spatial and temporal aggregations, the real (simulated) population
distributions to samples from fisheries-dependent and fisheries independent
catches to test if these are a true reflection of the relative density of the
populations. We then iii) simulate a fishery closure to protect a species based
on different spatial and temporal data aggregations. \\

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{\tilde{y},c}$ is the annual recruits in year $y$ for cell $c$. \\

@@

Recruitment is modelled as a function of adult biomass. In
\textit{MixFishSim}, it can either take the form of a stochastic Beverton-Holt
stock recruitment relationship, or a stochastic Ricker stock recruitment
relationship. The Beverton-Holt relationship is defined as\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, the stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases.

@@

Population movement is a combination of directed (advective) movement where at
certain times of year the population moves towards spawning grounds by
increasing the probabilities of moving into the spawning grounds from adjacent
cells, and random (diffusive) movement, governed by a stochastic process where
movement between adjacent cells is described by a set of probabilities.\\

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
\textit{Matérn} covariance structure, where the correlation strength weakens
with distance. This enables us to model the spatial autocorrelation observed in
animal populations where density is more similar in nearby locations
\citep{Tobler1970, F.Dormann2007, Poos2007} and we change the parameters to
implement different spatial structures for the different populations using the
\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
habitat field and combine it with a temporally dynamic thermal tolerance field to
imitate two key drivers of population dynamics. Each population was initialised
at a single location, and subsequently moved across the entire space according
to a probabilistic distribution based on habitat suitability (represented by
the normalised values
from the GRFs), temperature and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
below). \\

During pre-defined weeks of the year the habitat suitability is modified with
user-defined spawning habitat locations, resulting in each population having
concentrated areas where spawning takes place. The populations then move towards
these cells in the weeks prior to spawning, resulting in directional movement
towards the spawning grounds. \\

A time-varying temperature covariate changes the interaction between
time and suitable habitat on a weekly time-step. Each population $p$ was
assigned a thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$
so that each cell and population temperature suitability is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma^2_{p}$ the mean and standard deviation of the population
temperature tolerance. \\

@@

Fleet dynamics can be broadly categorised into three components: fleet
targeting - that determined the fleet catch efficiency and preference towards a
particular species; trip-level decisions, that determines the initial location
to be fished at the beginning of a trip; and within-trip decisions, that
determines movement from one fishing spot to another within a trip. An
explore-exploit type strategy was implemented in the model that combined these
three components for individual vessels to maximise their catch from an unknown
resource distribution \citep{Bailey2018}. The decision to use an individual
based model for fishing vessels was taken because fishers are heterogeneous in
their location choice behaviour due to different objectives, risk preference
and targeting preference \citep{VanPutten2012a}. Therefore in the simulations
fleet dynamics reflect individual experiences rather than pre-defined group
dynamics.

@@

Each fleet of \textit{n} vessels was characterised by both a general
efficiency, $Q_{fl}$, and a population specific efficiency, ${Q_{fl, p}}$ which
are each bound by [0,1]. The product of these parameters [$Q_{fl} \cdot
Q_{fl, p}$] affects the overall catch rates for the fleet and the preferential
targeting of one population over another. This, in combination with the
parameter choice for the step-function defined below (as well as some
randomness from the exploratory fishing process) determined the preference of
fishing locations for the fleet.

\subsubsection{Decision about where to fish at the start of the trip}

Several studies \citep[for a review]{Girardin2016} have confirmed past activity
and past catch rates are strong predictors of fishing location choice. For this
reason, the fleet dynamics sub-model included a learning component, where a
vessel's initial fishing location in a trip was based on selecting from
previously successful fishing locations. This was achieved by calculating an
expected revenue based on the catches from locations fished in the preceding
trip as well as the same month periods in previous years and the travel costs
from the port to the fishing grounds. Then a vessel chooses randomly from the
top 75 \% of fishing events as defined by the expected profit, that has a
seasonal component.

\subsubsection{Decision about where to fish within the trip}

@@

Fishing locations were chosen based on random search and, with increasing
proportion as time progressed, experience of profitable catches built up in the
same month from previous years and from the previous trip.  'Profitable' in
this context was defined as the locations where the top 70 \% of expected
profit would be found given revenue from previous trips and cost of movement to
the new fishing location. This probability was based on a logistic sigmoid
function with a lower asymptote of 0 and upper asymptote of 0.95, and a growth
rate that ensures the upper asymptote (where decisions are mainly based on past
knowledge) is reached approximately halfway through the simulation.  \\

@@

Individual habitat preferences and thermal tolerances result in different
spatial habitat use for each population (Figure \ref{fig:9}) and consequently
different seasonal exploitation patterns (Figure \ref{fig:10}).

@@

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
that may differ from the underlying populations [[\citep{Gillis2008}]]. As
such, we favoured a minimum realistic model of the fish populations
\citep{Plaganyi2014} taking account of environmental but not demographic
stochasticity, while incorporating detailed fishing dynamics that take account
of different drivers in a mechanistic way.  \\
